Wibbly Wobbly Timely Wimely Questions: \\Classifying Timely And Timeless Questions

### 2021-09-19 paper/main.tex
Addressed comment 3, motivating string comparison

>>>>

In order to determine whether answers to a question change over time, they must
be compared. While exact matching is an obvious option, it doesn't allow nuances
in representing names, places, and more. To give examples of common answer
types, "France" and "Paris France" wouldn't match, nor would "Dolly Parton" and
"Parton". With this binary, all-or-nothing approach to answer comparison,
answers representing the same idea aren’t recognized as similar. For these
reasons, we chose to compare answers using Levenshtein Distance and BLEU scores.
Both measurements provide matching scores on a scale from 0 to 100, allowing
recognition for varying amounts of matching content. This is especially
important for longer answers, which are also included within the NQ dataset.
